\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-04-04 popl-2019-journal-v/paper.tex
[POPLjv] Add split oLCM interpretation

@@

\subsection{Components, linking, programs, and contexts }
The executable configuration describes the machine state, but it does not make it clear what components run on the machine and how they interact with each other.
To clarify this, we introduce notions of components and programs from which we construct executable configurations.
A component (defined in Figure~\ref{fig:target-component-and-linking}) is basically a program with entry points in the form of imports that need to be linked.
It has exports that can satisfy the imports of other components.
% Structure
A base component $\comp_0$ consists of a code memory segment, a data memory segment, a list of imported symbols, a list of exported symbols, two lists specifying the available seals\footnote{We will return to the seals in Section~\ref{sec:form-secur-with}.}, and a set of all the linear addresses (addresses governed by a linear capability).
The import list specifies where in memory imports should be placed, and imports are matched to exports via their symbols.
The exports are words each associated with a symbol.
%base = library
A component is either a library component (without a main entry point) or an incomplete program with a main in the form of a pair of sealed capabilities.
The latter can be seen as a program that still needs to be linked with libraries.
% Linking .
Components are combined into new components by linking them together, as long as only one is an incomplete program with a main.
Two components can be linked when their memories, seals, and linear addresses are disjoint.
They are combined by taking the union of each of their constituents.
For every import that is satisfied by an export of the other component, the data memory is updated to have the exported word on the imported address.
The satisfied imports are removed from the import list in the resulting linked component and the exports are updated to be the exports of the two components.

@@

@@

\end{document}

>>>>

\begin{jversion}
% The remaining instructions
The interpretation of the remainder of the instructions are displayed in Appendix~\ref{app:instr-interpretation}. The instructions $\tgetb{}{}$, $\tgete{}{}$, $\tgetlin{}{}$, and $\tgetp{}{}$ all project information about capabilities. The $\tgetb{}{}$ instruction projects the base address of the range of authority, and $\tgete{}{}$ projects the end address of the range of authority. The linearity of a permission is projected with $\tgetlin{}{}$, and finally the permission is projected with $\tgetp{}{}$. The instructions $\tgetb{}{}$ and $\tgete{}{}$ also works on sets of seals. The instruction $\tisptr{}{}$ gives the type of a word which allows programs to be defensive in the sense that they can check whether a word is a capability before they use the word as one. \trgcm{} also has arithmetic instructions $\tplus{}{}{}$, $\tminus{}{}{}$, and $\tlt{}{}{}$. The latter instruction compares two numbers and writes 1 or 0 to a target register depending on whether one number is less than the other. The instruction $\tsetatob{}$ sets the current address (or seal) of a capability (or set of seals) to the base address of the range of authority (or range of seals). This instruction makes it possible to work relatively to the base address of a capability rather than with fixed addresses. While this instruction is not strictly necessary as it can be emulated with other instruction, it still seems useful in the case where you receive capabilities from an untrusted source. Finally, we have the $\trestrict{}{}$ instruction which  restricts the permission of a capability but only according to the $\le$ relation.
\end{jversion}

@@

\subsection{Components, linking, programs, and contexts }
\label{subsed:components-linking}
The executable configuration describes the machine state, but it does not make it clear what components run on the machine and how they interact with each other.
To clarify this, we introduce notions of components and programs from which we construct executable configurations.
A component (defined in Figure~\ref{fig:target-component-and-linking}) is basically a program with entry points in the form of imports that need to be linked.
It has exports that can satisfy the imports of other components.
% Structure
A base component $\comp_0$ consists of a code memory segment, a data memory segment, a list of imported symbols, a list of exported symbols, two lists specifying the available seals\footnote{We will return to the seals in Section~\ref{sec:form-secur-with}.}, and a set of all the linear addresses (addresses governed by a linear capability).
The import list specifies where in memory imports should be placed, and imports are matched to exports via their symbols.
The exports are words each associated with a symbol.
%base = library
A component is either a library component (without a main entry point) or an incomplete program with a main in the form of a pair of sealed capabilities.
The latter can be seen as a program that still needs to be linked with libraries.
% Linking .
Components are combined into new components by linking them together, as long as only one is an incomplete program with a main.
Two components can be linked when their memories, seals, and linear addresses are disjoint.
They are combined by taking the union of each of their constituents.
For every import that is satisfied by an export of the other component, the data memory is updated to have the exported word on the imported address.
The satisfied imports are removed from the import list in the resulting linked component and the exports are updated to be the exports of the two components.

@@

    \tsplit{r_1}{r_2}{r_3}{\rn}                  & $\sourcecolor\left.\updPcAddr{}\arraycolsep=0pt\array[t]{rl}(\Phi&\updReg{r_3}{0} \\ &\updReg{r_1}{c_1}\\ &\updReg{r_2}{c_2})\endarray\right.$ & \srcalt{$\Phi(r_3) = \stkptr{\perm,\baddr,\eaddr,\aaddr}$ and $\Phi(\rn) = n \in \nats$ and $\baddr \le n < \eaddr$ and $c_1 = \stkptr{\perm,\baddr,n,\aaddr}$ and $c_2 = \stkptr{\perm,n+1,\eaddr,\aaddr}$}\\

@@

\clearpage
\appendix
\input{appendix}
\end{document}
